Jeff Goldsmith

### 2019-11-25 teaching.Rmd
link to this workshop kinda thing

2018: Webinar: ["Data Science and Predictive Models in Public Health"]() and accompanying [reproducible lasso example](resources/lasso_example.zip) (webinar requires registration of free account)

>>>>

2019: [Workshop on website development](http://jeffgoldsmith.com/ehs_workshop/index.html)
2018: Webinar: ["Data Science and Predictive Models in Public Health"]() and accompanying [reproducible lasso example](resources/lasso_example.zip) (webinar requires registration of free account)
